Secure Composition of Robust and Optimising Compilers

### 2023-06-30 popl/main.tex
Move positioning lib to cmds.tex
note forme
Add author

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Matthis Kruse}
% \authornote{Both authors contributed equally to this research.}
\email{matthis.kruse@cispa.de}
\orcid{0000-0003-4062-9666}
\affiliation{%
  \institution{CISPA Helmholtz Center for Information Security}
  \streetaddress{Stuhlsatzenhaus 5}
  \city{Saarbr{\"u}cken}
  \state{Saarland}
  \country{Germany}
  \postcode{66123}
}

@@

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Kruse and Patrignani}

@@

      \draw[thick,dotted,->] (S) to[bend right=33,sloped] node[align=center,font=\scriptsize] {\gls{ms}\\ \Cref{thm:ccab:rtp:ms}} (M);
      \draw[thick,dotted,->] (M) to[bend right=0,sloped] node[align=center,font=\scriptsize] {\gls{ms}\\ \Cref{thm:cccfccdce:rtp:ms}} (E);
      \draw[thick,dotted,->] (S) to[out=-45,in=198,sloped] node[align=center,font=\scriptsize] {\gls{ms}\\ \Cref{thm:ccall:rtp:msscct}} (O);

>>>>

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Matthis Kruse}
% \authornote{Both authors contributed equally to this research.}
\email{matthis.kruse@cispa.de}
\orcid{0000-0003-4062-9666}
\affiliation{%
  \institution{CISPA Helmholtz Center for Information Security and Saarland University}
  \streetaddress{Stuhlsatzenhaus 5}
  \city{Saarbr{\"u}cken}
  \state{Saarland}
  \country{Germany}
  \postcode{66123}
}

\author{Michael Backes}
\email{director@cispa.de}
%\orcid{0000-0002-7130-9211}
\affiliation{%
  \institution{CISPA Helmholtz Center for Information Security}
  \streetaddress{Stuhlsatzenhaus 5}
  \city{Saarbr{\"u}cken}
  \state{Saarland}
  \country{Germany}
  \postcode{66123}
}

@@

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Kruse, Backes, and Patrignani}

@@

      \draw[thick,dotted,->] (S) to[bend right=33,sloped] node[align=center,font=\scriptsize] {\gls{ms}\\ \Cref{thm:ccab:rtp:ms}} (M);
      \draw[thick,dotted,->] (M) to[bend right=0,sloped] node[align=center,font=\scriptsize] {\gls{ms}\\ \Cref{thm:cccfccdce:rtp:ms}} (E);
      \draw[thick,dotted,->] (S) to[out=-45,in=198,sloped] node[align=center,font=\scriptsize] {\gls{ms}+\gls{scct}\\ \Cref{thm:ccall:rtp:msscct}} (O);
